The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-27 paper/sections/results.tex
mentioned collision and fixed typo

For raycasting operations and rendering we rely on Embree~\cite{10.1145/2601097.2601199} and Blender~\cite{blender}, and triangulate the NURBS surfaces, which only represents an implementation simplification. 
Our algorithm is not dependent on triangulating the boundary, and an ideal alternative would be using a path tracer that directly accepts NURBS geometry.

@@

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.

>>>>

For raycasting operations and rendering we rely on Embree~\cite{10.1145/2601097.2601199} and Blender~\cite{blender}, and triangulate the NURBS surfaces, which only represents an implementation simplification. 
Our algorithm is not dependent on triangulating the boundary, and an ideal alternative would be using a path tracer that directly accepts NURBS geometry.
For collision detection and handling, we use the triangulation to detect inter-penetrations at the beginning of every iteration, and attempt to move the collided vertex out of its collision surface using a spring-like penalty force, similar to \cite{10.1145/3355089.3356486, 10.1145/2010324.1964932}.

@@

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior is emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.
